---
title: "Shelter Dogs"
author: "ADS Project 5 Group 10"
output: html_document
---

##Introduction
Every year 7.6 million companion animals enter shelters every year. With 13,600 shelters nationwide, it is could be considered a large buisness empire. So what happens to all the dogs that enter the shelter? We decided to investigate what factors could potentially determine the likelyhood of a dog's outcome.

##Dataset preparation
Our data is taken from Kaggles' Shelter competition. This data composes information from one shelter in Austin, Texas between the spam of 2013 to 2015. It includes over 30000 domistic animals. In this study, we focused particularily on dogs. 

The data set originally contained 20 attributes. In particular, Breed and Color contained over 3000 unique factors. After refactoring these columns, we have 36 types of dogs along with 30 different colors. Please reference "../lib/Data Preparation Code.R".

```{r setup, include=FALSE}

library(ggplot2)
library(plotly)
library(dplyr)
library(networkD3)
library("colorspace") 
source('../lib/simplify_breeds.R')

# get shelter data
load("../data/shelter_data_new.RData")
```

* Original 
```{r, echo = FALSE}
colnames(shelter_data_new)[1:20]
```

* New
```{r, echo = FALSE}
colnames(shelter_data_new)
```

##Outcome Type
We started to look at the frequency of the outcome. As shown below, the largest four components are adoption, transfer, return to owner, and euthanasia. Because the other components make up a small component, we set a primary forcus on the others. 


```{r Pie Chart of Outcome, echo=FALSE, message=FALSE, warning=FALSE}
data<-shelter_data_new
Outcome <- data.frame(Type = data$'Outcome Type') %>% filter(Type != "")
Outcome <-Outcome %>% 
  group_by(Type) %>%
  summarise(freq = length(Type))

m <- list(l = 50, r = 50, b = 50, t = 50, pad = 4)
o_piechart <- plot_ly(Outcome, labels = ~Type, values = ~freq, type = 'pie',marker = list(colors = terrain_hcl(9))) %>%
  layout(title = 'Percentage of Outcome',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE)) %>%
  layout(autosize = F, width = 900, height = 450, margin = m)
o_piechart
```

##Dataset vs.Outcome 

###Seasonality
To start, we looked at the seasonality of the animals in the shelter. From the graph, we noticed that there seems to be some seasonality between the animals. However, when we furthered divided the animals we noticed there is a large seasonlity component for cats. This is not present for dogs. We can conclude there is very little seasonality for dogs. 

```{r seasonality graph, echo=FALSE, message=FALSE, warning=FALSE}
animal.num<-function(dataset){
  record_time<-seq(as.Date("2013-10-01"),as.Date("2015-09-30"),by="day")
  n<-length(record_time)
  
  take_in_num<-vector()
  for (i in 1:n){
  take_in_num[i]<-length(which(dataset$`Intake Date`<= record_time[i]))
  }

  take_out_num<-vector()
  for (i in 1:n){
  take_out_num[i]<-length(which(dataset$`Outcome Date`<= record_time[i]))
  }
  animal_in_shelter<-take_in_num-take_out_num
  return(data.frame(record_time,animal_in_shelter))
}

all_type_animal_num<-animal.num(data)

animal.type.num<-function(dataset){
  
  dog_data<-dataset[which(dataset$`Animal Type`=="Dog"),]
  cat_data<-dataset[which(dataset$`Animal Type`=="Cat"),]
  livestock_data<-dataset[which(dataset$`Animal Type`=="Livestock"),]
  other_data<-dataset[which(dataset$`Animal Type`=="Other"),]
  bird_data<-dataset[which(dataset$`Animal Type`=="Bird"),]
  
  dog_num<-animal.num(dog_data)
  cat_num<-animal.num(cat_data)
  livestock_num<-animal.num(livestock_data)
  other_num<-animal.num(other_data)
  bird_num<-animal.num(bird_data)
  
  hehe<-data.frame(dog_num,cat_num[,2],livestock_num[,2],other_num[,2],bird_num[,2])
  colnames(hehe)<-c("Record Time",unique(data$`Animal Type`))
  
  return(hehe)
}

group_animal_num<-animal.type.num(data)
group_animal_num$All <- all_type_animal_num$animal_in_shelter

Seasonality<-plot_ly(group_animal_num, x=~`Record Time`, y=~Dog,
        type = 'scatter', mode = 'lines',name='Dogs',
        line = list(color = 'rgb(126, 172, 247)', width = 2),visible = "legendonly")%>%
  add_trace(y=~Cat,type = 'scatter', mode = 'lines',name='Cats',
        line =  list(color = 'rgb(110, 209, 146)', width = 2),visible = "legendonly")%>%
  add_trace(y=~Livestock,type='scatter', mode = 'lines',name='Livestock',
        line =  list(color = 'rgb(216, 137, 110)', width = 2),visible = "legendonly")%>%
  add_trace(y=~Other,type='scatter', mode = 'lines',name='Other',
        line =  list(color = 'rgb(149, 153, 193)', width = 2),visible = "legendonly")%>%
  add_trace(y=~Bird,type='scatter', mode = 'lines',name='Birds',
        line =  list(color = 'rrgb(244, 220, 66)', width = 2),visible = "legendonly")%>%
  add_trace(y=~All,type='scatter', mode = 'lines',name='All',
        line =  list(color = "red", width = 3),visible = TRUE) %>%
  layout(title = "Numbers of group in shelter over time",
          xaxis = list(
          rangeselector = list(
            buttons = list(
              list(count = 3,label = "3 mo",step = "month",stepmode = "backward"),
              list(count = 6,label = "6 mo",step = "month",stepmode = "backward"),
              list(count = 1,label = "1 yr",step = "year",stepmode = "backward"),
              list(step = "all"))),
          rangeslider = list(type = "date")),
          yaxis = list(title = "",showgrid = FALSE,zeroline = FALSE,showline = FALSE)) %>%
  layout(autosize = F, width = 900, height = 450)
Seasonality
```


###Days in shelter VS. Outcome
We also anaylized how the number of days in the shelter affected the outcome of the dog. From the graph, we can note that majority of the dogs stay for less than 10 days. For dogs who return to owners, they are more quickly returned than dogs who are adopted.

```{r shelter days vs outcome, echo=FALSE, message=FALSE, warning=FALSE}
dog_data<-data[which(data$`Animal Type`=="Dog"),]

out.days<-function(dataset){
  
  dog_days_in_shelter<-as.Date(dataset$`Outcome Date`,"%y-%m-%d")-
    as.Date(dataset$`Intake Date`,"%y-%m-%d")
  
  #Check for the error then correct them 
  dog_days_in_shelter[which(dog_days_in_shelter<0)]=
    abs(dog_days_in_shelter[which(dog_days_in_shelter<0)])
  
  out_days<-data.frame(dog_days_in_shelter,dog_data$`Outcome Type`)[which(
    dataset$`Outcome Type`=="Return to Owner"|
    dataset$`Outcome Type`=="Transfer"|
    dataset$`Outcome Type`=="Adoption"|
    dataset$`Outcome Type`=="Euthanasia"
  ),]
  
  out_days[,2]<-as.factor(as.character(out_days[,2]))
  out_days<-data.frame(as.numeric(out_days[,1]),out_days[,2])
  colnames(out_days)<-c("Days","Outcome.Type")
  
  return(out_days)
}

out_days<-out.days(dog_data)

shelter_days<-plot_ly(out_days, y = ~Days, x = ~Outcome.Type, color = ~Outcome.Type, type = 'box')%>%
  layout(title='Days in shelter vs Outcome type') %>%
  layout(autosize = F, width = 900, height = 450)
shelter_days
```


###Dog name VS. Outcome
We then analyzed if a dog has a name, how it will affect its outcome. As we can see, there seem to be a higher rate of being returned to owner if the dog has a name. There is also a significant increase for a dog to be transferred if it has no name. The adoption rate, however remains the same. 

```{r names vs. outcome, echo=FALSE, message=FALSE, warning=FALSE}
# Dogs names vs outcome
# deal with the data

percent.out.name<-function(dataset){
  
  out_name<-matrix(nrow = 4 ,ncol = 2)
  colnames(out_name)<-c("Have Name","No Name")
  rownames(out_name)<-c("Return to Owner","Transfer",
                     "Adoption","Euthanasia")

 for (i in 1:4){
     out_name[i,1]<-length(which(dataset$Name!=""&
                                 dataset$`Outcome Type`==rownames(out_name)[i]))/length(which(dataset$Name!=""))
     out_name[i,2]<-length(which(dataset$Name == "" &dataset$`Outcome Type`==rownames(out_name)[i]))/
       length(which(dataset$Name==""))
 }
  return(data.frame(round(out_name*100,1)))
}

#Create the data

out_name<-percent.out.name(dog_data)

name <- plot_ly(out_name, x = ~Have.Name, y = ~reorder(rownames(out_name), Have.Name),
              name = 'Dogs who have a name',
              type = 'bar', orientation = 'h',
              marker = list(color = 'rgba(50, 171, 96, 0.6)',
                            line = list(color = 'rgba(50, 171, 96, 1.0)', width = 1))) %>%
  layout(yaxis = list(title = "",showgrid = FALSE, 
                      showline = FALSE, showticklabels = TRUE, domain= c(0, 0.85)),
         xaxis = list(zeroline = FALSE, showline = FALSE, showticklabels = TRUE, showgrid = TRUE))

no_name <-plot_ly(out_name, x = ~No.Name, y = ~reorder(rownames(out_name), Have.Name),
              name = 'Dogs who have no name',
              type = 'bar', orientation = 'h',
              marker = list(color = 'rgba(245, 182, 140,0.6)',
                            line = list(color = 'rgba(245, 182, 140,0.6)', width = 1))) %>%
  layout(yaxis = list(showgrid = FALSE, showline = TRUE, 
                      showticklabels = FALSE,domain= c(0, 0.85)),
         xaxis = list(zeroline = FALSE, showline = FALSE, 
                      showticklabels = TRUE, showgrid = TRUE,side = 'top'))

subplot(name, no_name) %>%
  layout(title = 'Dog Names VS. Outcome',
         legend = list(x = 0.01, y = 1.038,
                       font = list(size = 10)),
         margin = list(l = 100, r = 20, t = 70, b = 70),
         paper_bgcolor = 'rgb(248, 248, 255)',
         plot_bgcolor = 'rgb(248, 248, 255)') %>%
  layout(autosize = F, width = 900, height = 450)

```


###Sex Vs. Outcome
We then noticed that the gender of the dog is divided into four categories: Neutered Male, Spayed Female, Intact Female, and Intact Male. For the dogs being returned to the owner, we noticed there is a larger spike for a specific dog to be a neutered male. All other categories remain the same. 

```{r Sex vs outcome, echo=FALSE, message=FALSE, warning=FALSE}
#Deal with the data
percent.out.sex<-function(dataset){
  out_sex<-matrix(nrow = 4 ,ncol = 4)
  colnames(out_sex)<-c("Neutered Male","Spayed Female","Intact Female","Intact Male")
  rownames(out_sex)<-c("Return to Owner","Transfer","Adoption","Euthanasia")

 for (i in 1:4){
   for (j in 1:4){
     out_sex[i,j]<-length(which(dataset$`Sex upon Intake`==colnames(out_sex)[j]&
                                 dataset$`Outcome Type`==rownames(out_sex)[i]))/
       length(which(dataset$`Outcome Type`==rownames(out_sex)[i]))
   }
 }
  out_sex<-data.frame(round(out_sex*100,1))
  
  return(out_sex)
}
out_sex<-percent.out.sex(dog_data)

#Plot
top_labels <- colnames(out_sex)

sex <- plot_ly(out_sex, x = ~Neutered.Male, y = rownames(out_sex), type = 'bar', orientation = 'h',
             marker = list(color = 'rgba(17, 4, 4, 0.8)',
                           line = list(color = 'rgb(248, 248, 249)', width = 1)),
             name='Neutered<br>Male') %>%
  add_trace(x = ~Spayed.Female, marker = list(color = 'rgba(165, 58, 16, 0.8)'),
            name='Spayed<br>Female') %>%
  add_trace(x = ~Intact.Female, marker = list(color = 'rgba(196, 101, 29, 0.8)'),
            name='Intact<br>Female') %>%
  add_trace(x = ~Intact.Male, marker = list(color = 'rgba(232, 167, 118, 0.85)'),
            name='Intact<br>Male') %>%
  layout(xaxis = list(title = "",showgrid = FALSE,showline = FALSE,showticklabels = FALSE,zeroline = FALSE,domain = c(0.15, 1)),
         yaxis = list(title = "",showgrid = FALSE,showline = FALSE,showticklabels = FALSE,zeroline = FALSE),
         title = "Sex Type upon Intake VS. Outcome",
         barmode = 'stack',
         paper_bgcolor = 'rgb(248, 248, 255)', plot_bgcolor = 'rgb(248, 248, 255)',
         margin = list(l = 120, r = 10, t = 140, b = 80)
         ) %>%
  # labeling the y-axis
  add_annotations(xref = 'paper', yref = 'y', x = 0.14, y = rownames(out_sex),
                  xanchor = 'right',
                  text = rownames(out_sex),
                  font = list(family = 'Arial', size = 12,
                              color = 'rgb(67, 67, 67)'),
                  showarrow = FALSE, align = 'right') %>%
  layout(autosize = F, width = 900, height = 450)
sex
```


###Dog Breeds

#### Frequency of breeds in shelter relative to their baseline frequency
Here we compare the frequency of each pure breed in the shelter relative to its baseline frequency in American homes. Positive values (red colors) indicate over-represented breeds in the shelter. These are, presumably, breeds more likely to be abandoned. Negative values (green) indicate the opposite.

```{r baseline comparision, warning=FALSE, message=FALSE, echo=FALSE}
D = shelter_data_new
D = D[D$`Animal Type`=='Dog',]
D$Breed = tolower(D$Breed)

# get baseline frequencies of breeds in U.S.
breeds = read.csv('../data/breed_count.csv')
breed_count = as.integer(gsub(',', '', breeds$count))
breeds_names = gsub('\\(', '', breeds$breed)
breeds_names = gsub('\\)', '', breeds_names)
breeds_names = gsub(' Imp', '', breeds_names)
breeds_names = tolower(breeds_names)
names(breed_count) = breeds_names
breed_count = breed_count[breed_count>0]

# simplify breeds
D$Breed = simplify_breeds(D$Breed)
names(breed_count) = simplify_breeds(names(breed_count))

# recount breeds after simplification
breed_count = tapply(breed_count, names(breed_count), sum)

# focus on pure breeds most common in shelter (n>9)
sh_breeds = table(D$Breed[!grepl('mix|/', D$Breed)])
sh_breeds = sh_breeds[sh_breeds>9]


# resolve conflicts between breed lists:
sh_breeds = sh_breeds[!names(sh_breeds)=='rat terrier']
sh_breeds = sh_breeds[!names(sh_breeds)=='anatol shepherd']
names(breed_count)[names(breed_count)=='retriever labrador'] = 'labrador retriever'
names(breed_count)[names(breed_count)=='retriever golden'] = 'golden retriever'
names(breed_count)[names(breed_count)=='german shepherd dog alsatian'] = 'german shepherd'
names(breed_count)[names(breed_count)=='poodle miniature'] = 'miniature poodle'
names(breed_count)[names(breed_count)=='poodle toy'] = 'toy poodle'
names(breed_count)[names(breed_count)=='dobermann'] = 'doberman pinsch'
names(breed_count)[names(breed_count)=='spaniel cocker'] = 'cocker spaniel'
names(breed_count)[names(breed_count)=='pyrenean mountain dog'] = 'great pyrenees'
names(breed_count)[names(breed_count)=='parson russell terrier'] = 'jack russell terrier'
names(breed_count)[names(breed_count)=='basset griffon vendeen petit'] = 'pbgv'

# compute relative frequencies of main breeds in shelter vs country
sh_breeds_freq = sh_breeds/sum(sh_breeds)
breeds_freq = breed_count[names(sh_breeds)]/sum(breed_count[names(sh_breeds)])
rel_freqs = sort(sh_breeds_freq/breeds_freq, decreasing=T)

# plot:
plot_freqs = as.data.frame(rel_freqs)
colnames(plot_freqs) = c('breed', 'val')

color_overrep = colorRampPalette(c('#ff7c7c', "black")) (sum(plot_freqs$val>1)) 
color_underrep = colorRampPalette(c("black", '#a2f2be')) (sum(plot_freqs$val<=1)) 

plot_ly(data = plot_freqs,
        x = ~breed,
        y = ~log(val),
        type = 'bar', 
        text = ~breed, 
        hoverinfo = 'text', 
        marker = list(color=c(color_overrep, color_underrep)), 
        width = 900) %>%
  layout(title = "Relative Frequency of Dog Breeds in Shelter",
         xaxis = list(title = "", tickangle = 45, position=.15, domain=c(0,.9)),
         yaxis = list(title = "<- Less than Expected | More than Expected ->                          .", 
                      domain=c(.13,1)))
```

Keeping in mind, this only shows pure breed dogs. We can see that there are selective dogs that are more likely to end up in the pound such as Austrilian Cattle Dog. Popular dogs such a goldren retriver appears less. 


####Breed VS. Outcome
We then studied if the dog breed function effects the outcome of the dog. In particular, we focuesed on adoption. After recategorizing the dogs based on breed, function, and mix. We categorized the dog into 36 categories. Then we got the outcome ratio. 

```{r breeds group vs outcome, echo=FALSE, message=FALSE, warning=FALSE}
outcome = c("Return to Owner","Transfer","Adoption","Euthanasia")

adoption_rate = data.frame(Breed = c(unique(D$Breed_New)), Adoption = 0, Euthanasia = 0, `Return to Owner` = 0, Transfer = 0)

for (i in 1:dim(adoption_rate)[1]){
  x = adoption_rate[i,]
  table = D %>% filter(`Outcome Type` %in% outcome) %>%
    filter(`Breed_New` == x$Breed) %>% group_by(`Outcome Type`) %>% summarise(count = n())
  freq = table$count/sum(table$count)
  if ("Adoption" %in% table$`Outcome Type`){
    adoption_rate$Adoption[i] = freq[which(table$`Outcome Type` == "Adoption")]
  }
  if ("Euthanasia" %in% table$`Outcome Type`){
    adoption_rate$Euthanasia[i] = freq[which(table$`Outcome Type` == "Euthanasia")]
  }
  if ("Return to Owner" %in% table$`Outcome Type`){
    adoption_rate$Return.to.Owner[i] = freq[which(table$`Outcome Type` == "Return to Owner")]
  }
  if ("Transfer" %in% table$`Outcome Type`){
    adoption_rate$Transfer[i] = freq[which(table$`Outcome Type` == "Transfer")]
  }
}

adoption_rate = adoption_rate[order(adoption_rate$Adoption),]
adoption_rate$Breed = factor(adoption_rate$Breed, levels = adoption_rate$Breed)

f1 = list(family = "Arial, sans-serif", size = 16, color = "lightgrey")
f2 = list(family = "Old Standard TT, serif", size = 10, color = "black")
a = list(titlefont = f1, showticklabels = TRUE, tickangle = 45, tickfont = f2,
         exponentformat = "E")
m <- list(l = 50, r = 50, b = 180, t = 50, pad = 4)
breed_plot <- plot_ly(adoption_rate, x = ~Breed, y = ~Adoption, type = 'bar', name = 'Adoption rate',
        marker = list(color = rainbow_hcl(4)[1],
                      line = list(width = 3))) %>%
    add_trace(y = ~Euthanasia, name = 'Euthanasia',
            marker = list(color = rainbow_hcl(4)[2],
                          line = list(width = 3))) %>%
    add_trace(y = ~Return.to.Owner, name = 'Return to Owner',
            marker = list(color = rainbow_hcl(4)[3],
                          line = list(width = 3))) %>%
    add_trace(y = ~Transfer, name = 'Transfer',
            marker = list(color = rainbow_hcl(4)[4],
                          line = list(width = 3))) %>%
  layout(barmode = 'stack',
         xaxis = list(title = ""),
         yaxis = list(title ="")) %>%
  layout(autosize = F, width = 900, height = 450, margin = m)
breed_plot

adoption_rate$Euthanasia_c <- adoption_rate$Euthanasia + adoption_rate$Adoption
adoption_rate$Return.to.Owner_c <- adoption_rate$Euthanasia + adoption_rate$Adoption + adoption_rate$Return.to.Owner
adoption_rate$Transfer_c <- adoption_rate$Euthanasia + adoption_rate$Adoption + adoption_rate$Transfer + adoption_rate$Return.to.Owner

# plot_ly(adoption_rate, x = ~Breed, y = ~Adoption, name = 'Adoption rate', type = 'scatter', mode = 'lines') %>%
#   add_trace(y = ~Euthanasia, name = 'Euthanasia rate', mode = 'lines') %>%
#   add_trace(y = ~Return.to.Owner, name = 'Return to Owner rate', mode = 'lines') %>%
#   add_trace(y = ~Transfer, name = 'Transfer rate', mode = 'lines') %>%
#   layout(title = 'Dog Breeds versus Outcome Type',
#          yaxis = list(title = ''), xaxis = a) %>% 
#          layout(autosize = F, width = 1000, height = 500, margin = m)
```
* Non-sporting & Others only consists of one dog

We noticed that hound dog seem to have the highest rate of adoption. And pure dogs, such as non-sporting, terrier and working, had high rate of return to owners.
```{r Adoption by rank}
rev(adoption_rate$Breed)
```
From the ranking, we can see that hounds type of dogs are more likely to be adopted. It also seems like non-sporting dogs will be less likely. 

##Transition Path
We furthered wanted to see the path a dog will take once it enters the shelter. The following three bars represent intake type, intake condition and outcome type, individually.

```{r sankey network, echo=FALSE, message=FALSE, warning=FALSE}
#Sankey network
#Create the data
sankey.data<-function(dataset){
  sdata<-dataset[which(
  dataset$`Outcome Type`=="Return to Owner"|
    dataset$`Outcome Type`=="Transfer"|
    dataset$`Outcome Type`=="Adoption"|
    dataset$`Outcome Type`=="Euthanasia"),]


  dog_nodes<-c(unique(dataset$`Intake Type`),unique(dataset$`Intake Condition`),
             "Return to Owner","Transfer","Adoption","Euthanasia" )
  dog_link<-matrix(nrow = 64, ncol = 3 )
  dog_link[,1]<-c(rep(0,8),rep(1,8),rep(2,8),rep(3,8),
                rep(4,4),rep(5,4),rep(6,4),rep(7,4),
                rep(8,4),rep(9,4),rep(10,4),rep(11,4))
  dog_link[,2]<-c(rep(4:11,4),rep(12:15,8))

  for (i in 1:64){
    if(i<=32){
      dog_link[i,3]<-length(which(sdata$`Intake Type`==dog_nodes[dog_link[i,1]+1] & 
               sdata$`Intake Condition`== dog_nodes[dog_link[i,2]+1]))
      }else{
        dog_link[i,3]<-length(which(sdata$`Intake Condition`==dog_nodes[dog_link[i,1]+1] &
                                      sdata$`Outcome Type`== dog_nodes[dog_link[i,2]+1]))
      }
  }
  colnames(dog_link)<-c("source","target","value")

  haha<-list()
  haha$nodes<-as.data.frame(dog_nodes)
  haha$links<-as.data.frame(dog_link)

  return(haha)
}

kk<-sankey.data(dog_data)
sankey<-sankeyNetwork(Links = kk$links, Nodes = kk$nodes, Source = "source",
              Target = "target", Value = "value", NodeID = "dog_nodes",
              units = "", fontSize = 12, nodeWidth = 40,nodePadding = 8,
              margin = NULL, height = 400, width = 800,
              colourScale = JS("d3.scale.category20()"))
sankey
```


##Dog Outcome Type Prediction
We now look at what characteristics make a dog more likely to be adopted. We ran a logistic regression to predict adoption outcome. Below we show, ranked by importance, the different predictors. Green indicates a positive influence of the predictor, red indicates a negative influence.   

```{r outcome prediction, warning=FALSE, message=FALSE, echo=FALSE}

# load relevant output of logistic regression:
load('../output/lrt_log_reg2.RData')

# plot
importance = lrt[-1,2]/lrt[-1,1]
names(importance) = rownames(lrt)[-1]
importance = sort(importance, decreasing=T)
importance = as.data.frame(as.table(importance))
colnames(importance) = c('pred', 'val')

colors = rep('#a2f2be', nrow(importance))
colors[importance$pred %in% c('Age','IsMale')] = '#ff7c7c' # change colors for predictors with neg influence based on logistic reg results

m <- list(l = 50, r = 50, b = 50, t = 50, pad = 4)
plot_ly(data = importance,
        x = ~pred,
        y = ~log(val),
        type = 'bar', 
        text = ~pred, 
        hoverinfo = 'text', 
        marker = list(color=colors, line=list(width = 1)), 
        height = 400) %>%
  layout(title = "Predictors of Adoption",
         xaxis = list(title = "", position=.1, domain=c(0,.9)),
         yaxis = list(title = "Importance [log(deviance/df)]", domain=c(.1,1))) %>%
  layout(autosize = F, width = 900, height = 450, margin = m)

```

##Prediction Result
 | Final Classifier | Testing Error Rate |
 |------|------|
 | GBM with 50 trees | 21% |
