---
title: "Shelter Dogs"
output: html_document
---

\
\

```{r setup, include=FALSE}

library(ggplot2)
library(plotly)
library(dplyr)
source('../lib/simplify_breeds.R')


```

#### Frequency of breeds in shelter relative to their baseline frequency
\

Here we compare the frequency of each pure breed in the shelter relative to its baseline frequency in American homes. Positive values (red colors) indicate over-represented breeds in the shelter. These are, presumably, breeds more likely to be abandoned. Negative values (green) indicate the opposite.
\


```{r analysis1, warning=FALSE, message=FALSE, echo=FALSE}

# get shelter data and keep dogs only
load("../data/shelter_data_new.RData")
D = shelter_data_new
D = D[D$`Animal Type`=='Dog',]
D$Breed = tolower(D$Breed)

# get baseline frequencies of breeds in U.S.
breeds = read.csv('../data/breed_count.csv')
breed_count = as.integer(gsub(',', '', breeds$count))
breeds_names = gsub('\\(', '', breeds$breed)
breeds_names = gsub('\\)', '', breeds_names)
breeds_names = gsub(' Imp', '', breeds_names)
breeds_names = tolower(breeds_names)
names(breed_count) = breeds_names
breed_count = breed_count[breed_count>0]

# simplify breeds
D$Breed = simplify_breeds(D$Breed)
names(breed_count) = simplify_breeds(names(breed_count))

# recount breeds after simplification
breed_count = tapply(breed_count, names(breed_count), sum)

# focus on pure breeds most common in shelter (n>9)
sh_breeds = table(D$Breed[!grepl('mix|/', D$Breed)])
sh_breeds = sh_breeds[sh_breeds>9]


# resolve conflicts between breed lists:
sh_breeds = sh_breeds[!names(sh_breeds)=='rat terrier']
sh_breeds = sh_breeds[!names(sh_breeds)=='anatol shepherd']
names(breed_count)[names(breed_count)=='retriever labrador'] = 'labrador retriever'
names(breed_count)[names(breed_count)=='retriever golden'] = 'golden retriever'
names(breed_count)[names(breed_count)=='german shepherd dog alsatian'] = 'german shepherd'
names(breed_count)[names(breed_count)=='poodle miniature'] = 'miniature poodle'
names(breed_count)[names(breed_count)=='poodle toy'] = 'toy poodle'
names(breed_count)[names(breed_count)=='dobermann'] = 'doberman pinsch'
names(breed_count)[names(breed_count)=='spaniel cocker'] = 'cocker spaniel'
names(breed_count)[names(breed_count)=='pyrenean mountain dog'] = 'great pyrenees'
names(breed_count)[names(breed_count)=='parson russell terrier'] = 'jack russell terrier'
names(breed_count)[names(breed_count)=='basset griffon vendeen petit'] = 'pbgv'

# compute relative frequencies of main breeds in shelter vs country
sh_breeds_freq = sh_breeds/sum(sh_breeds)
breeds_freq = breed_count[names(sh_breeds)]/sum(breed_count[names(sh_breeds)])
rel_freqs = sort(sh_breeds_freq/breeds_freq, decreasing=T)

# plot:
plot_freqs = as.data.frame(rel_freqs)
colnames(plot_freqs) = c('breed', 'val')

color_overrep = colorRampPalette(c('#ff7c7c', "black")) (sum(plot_freqs$val>1)) 
color_underrep = colorRampPalette(c("black", '#a2f2be')) (sum(plot_freqs$val<=1)) 

plot_ly(data = plot_freqs,
        x = ~breed,
        y = ~log(val),
        type = 'bar', 
        text = ~breed, 
        hoverinfo = 'text', 
        marker = list(color=c(color_overrep, color_underrep), line=list(color='rgb(0,0,0)', width = 1)), 
        width = 900) %>%
  layout(title = "Relative Frequency of Dog Breeds in Shelter",
         xaxis = list(title = "", tickangle = 45, position=.15, domain=c(0,.9)),
         yaxis = list(title = "<- Less than Expected | More than Expected ->                          .", 
                      domain=c(.13,1)))
```
\
\


#### Predicting dog adoption
\

We now look at what characteristics make a dog more likely to be adopted. We ran a logistic regression to predict adoption outcome. Below we show, ranked by importance, the different predictors. Green indicates a positive influence of the predictor, red indicates a negative influence.   
\

```{r analysis2, warning=FALSE, message=FALSE, echo=FALSE}

# load relevant output of logistic regression:
load('../output/lrt_log_reg.RData')

# plot
importance = lrt[-1,2]/lrt[-1,1]
names(importance) = rownames(lrt)[-1]
importance = sort(importance, decreasing=T)
importance = as.data.frame(as.table(importance))
colnames(importance) = c('pred', 'val')

colors = rep('#a2f2be', nrow(importance))
colors[importance$pred %in% c('Age','IsMale')] = '#ff7c7c' # change colors for predictors with neg influence based on logistic reg results

plot_ly(data = importance,
        x = ~pred,
        y = ~log(val),
        type = 'bar', 
        text = ~pred, 
        hoverinfo = 'text', 
        marker = list(color=colors, line=list(color='rgb(0,0,0)', width = 1)), 
        height = 400) %>%
  layout(title = "Predictors of Adoption",
         xaxis = list(title = "", position=.1, domain=c(0,.9)),
         yaxis = list(title = "Importance [log(deviance/df)]", domain=c(.1,1)))

```

